---
title: "R Notebook"
output: html_notebook
---

##Step 1: Load data and libraries
```{r}
library(plyr)
load("/Users/ouminamikun/Documents/Columbia/Spring 2017/ADS/final project/dat.RData")
```

##Step 2: ranking
```{r}
movie_agg <- aggregate(dat$rating, list(dat$movie_name), mean)
colnames(movie_agg) <- c("movies", "avg_rating")

users_count <- aggregate(dat$movie_name,list(dat$movie_name), length)
movie_agg$users_count <- users_count$x
movie_agg <- movie_agg[order(movie_agg$avg_rating, decreasing = T), ]

nopop <- movie_agg[movie_agg$users_count <= 6,]
nopop_hrated <- head(nopop$movies, 10)
pop <- movie_agg[movie_agg$users_count >=76,]
pop_lrated <- rev(tail(pop$movies, 10))

top50 <- head(movie_agg$movies[movie_agg$users_count >= 250],50)
worst50 <- rev(tail(movie_agg$movies, 50))

top50_s <- top50[1]
for(i in 2:length(top50)){
  top50_s <- paste(top50_s,top50[i], sep = "\n")
}


pop_lrated_s <- pop_lrated[1]
for(i in 2:length(pop_lrated)){
  pop_lrated_s <- paste(pop_lrated_s, pop_lrated[i], sep = "\n")
}

nopop_hrated_s <- nopop_hrated[1]
for(i in 2:length(nopop_hrated)){
  nopop_hrated_s <- paste(nopop_hrated_s, nopop_hrated[i],sep = "\n")
}
```

```{r}
library(omdbapi)
library(dplyr)
library(rvest)
library(RCurl)
library(jpeg)

lego_movie <- read_html("http://www.imdb.com/title/tt1490017/")
poster <- lego_movie %>%
  html_nodes(".poster img") %>%
  html_attr("src")
poster

A <- find_by_title("Game of Thrones", type="series", season=1, episode=1)

A$imdbRating
A$Plot
A$Poster

B <- find_by_title("Annie Hall")
b <- B$Poster
b[1]


pic <- readJPEG(getURLContent(b[2]))
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
ah <- rasterImage(pic,0,0,1,1)


```
```{r}


```

## Shiny app
```{r}
library(omdbapi)
library(dplyr)
library(rvest)
library(RCurl)
library(jpeg)
library(shiny)
library(shinydashboard)

ui <- dashboardPage(
  dashboardHeader(),
  
  dashboardSidebar(
    sidebarMenu(
      menuItem("Dashboard", tabName = "dashboard", icon = icon("dashboard"))
    )
  ),
  
  dashboardBody(
      tabItem(tabName = "dashboard",
              fluidRow(
                box(title = "Top 1", 
                    background = "red",
                    status = "danger", 
                    width = 3,
                    solidHeader = TRUE,
                    plotOutput("top1", height = 250)),
                box(title = "Top 2", 
                    background = "red",
                    status = "danger", 
                    width = 3,
                    solidHeader = TRUE,
                    plotOutput("top2", height = 250)),
                box(title = "Top 3",
                    background = "red",
                    width = 3,
                    status = "danger",
                    plotOutput("top3"), height = 250),
                box(title = "Top 4",
                    background = "red",
                    width = 3,
                    status = "danger",
                    plotOutput("top4"),height = 250),
                box(title = "Top 50",
                    status = "primary",
                    solidHeader = TRUE,
                    collapsible = TRUE,
                    verbatimTextOutput("top50")),
                box(title = "Popular but bad movies",
                    status = "success",
                    solidHeader = T,
                    verbatimTextOutput("pop_lrated")),
                box(title = "Not popular but great movies",
                    status = "danger",
                    solidHeader = T,
                    verbatimTextOutput("nopop_hrated"))
                
                
                
                )
              )
      
    )
  )


server <- function(input, output) { 

  output$top50 <- renderText({top50_s })
  output$pop_lrated <- renderText({pop_lrated_s})
  output$nopop_hrated <- renderText({nopop_hrated_s})
  output$top1 <- renderPlot({showposter("Everyone Says I Love You")})
  output$top2 <- renderPlot({showposter("What's Eating Gilbert Grape")})
  output$top3 <- renderPlot({showposter("Legends of the Fall")})
  output$top4 <- renderPlot({showposter("Mighty Aphroditee")})
  output$top5 <- renderPlot({showposter("Snow White and the Seven Dwarfs ")})
  
  }

shinyApp(ui = ui, server = server)


